Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-06 doc/slides/hong+eisner.TLT13.slides.tex
updated parse visualization explanations

\begin{figure}
\begin{subfigure}[b]{0.4850\textwidth}
	\begin{dependency}
		\begin{deptext}
			the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
			- \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
		\end{deptext}
		\depedge[edge above, edge style = {red}]{2}{3}{S}
		\depedge[edge above, edge style = {red}]{3}{6}{I}
		\depedge[edge above, edge style = {red}]{2}{1}{D}
		\depedge[edge above, edge style = {red}]{7}{8}{MV}
		\depedge[edge above, edge style = {red}]{6}{7}{P}
		\depedge[edge above, edge style = {red}]{8}{9}{J}
		\deproot[edge above, edge style = {red}]{2}{W}
		\deproot[edge above, edge style = {red}]{7}{WV}
		\deproot[edge above, edge style = {red}]{10}{X}
		\depedge[edge above, edge style = {red}]{6}{4}{E}
		\depedge[edge above, edge style = {red}]{6}{5}{E}
	\end{dependency}
\end{subfigure}

\end{figure}
\NoteJH{figure not centered}
\NoteJH{Make the edges undirected}

@@

\frame{\frametitle{Link Grammars}
\begin{figure}
\begin{subfigure}[b]{0.4850\textwidth}
	\begin{dependency}
		\begin{deptext}
			{\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
			the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
			- \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
		\end{deptext}
		\deproot[edge above, edge style = {blue, dotted}]{3}{\small ROOT}
		\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
		\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
		\depedge[edge above, edge style = {blue, dotted}]{3}{4}{\small ADV}
		\depedge[edge above, edge style = {blue, dotted}]{3}{5}{\small ADV}
		\depedge[edge below, edge style = {red, thick}]{3}{6}{I}
		\depedge[edge above, edge style = {blue, thick}]{3}{6}{\small VC}
		\depedge[edge above, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
		\depedge[edge below, edge style = {red, thick}]{2}{1}{D}
		\depedge[edge above, edge style = {blue, thick}]{2}{1}{\small NMOD}
		\depedge[edge below, edge style = {red, thick}]{7}{8}{MV}
		\depedge[edge above, edge style = {blue, thick}]{7}{8}{\small ADV}
		\depedge[edge below, edge style = {orange, thick}]{6}{7}{P}
		\depedge[edge above, edge style = {blue, thick}]{6}{7}{\small VC}
		\depedge[edge below, edge style = {red, thick}]{8}{9}{J}
		\depedge[edge above, edge style = {blue, thick}]{8}{9}{\small PMOD}
		\deproot[edge below, edge style = {red, dotted}]{2}{W}
		\deproot[edge below, edge style = {orange, ultra thick, dotted}]{7}{WV}
		\deproot[edge below, edge style = {red, dotted}]{10}{X}
		\depedge[edge below, edge style = {red, dotted}]{6}{4}{E}
		\depedge[edge below, edge style = {red, dotted}]{6}{5}{E}
	\end{dependency}
\end{subfigure}

\end{figure}

>>>>

\begin{figure}
  \begin{dependency}[edge style={-}]
	\begin{deptext}
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\depedge[edge above, edge style = {red}]{2}{3}{S}
	\depedge[edge above, edge style = {red}]{3}{6}{I}
	\depedge[edge above, edge style = {red}]{2}{1}{D}
	\depedge[edge above, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, edge style = {red}]{6}{7}{P}
	\depedge[edge above, edge style = {red}]{8}{9}{J}
	\deproot[edge above, edge style = {red}]{2}{W}
	\deproot[edge above, edge style = {red}]{7}{WV}
	\deproot[edge above, edge style = {red}]{10}{X}
	\depedge[edge above, edge style = {red}]{6}{4}{E}
	\depedge[edge above, edge style = {red}]{6}{5}{E}
  \end{dependency}
  \caption{Link Parse of a sentence from Penn Tree Bank}
\end{figure}

@@

\frame{\frametitle{Link Grammars}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\depedge[edge above, edge style = {red}]{2}{3}{S}
	\depedge[edge above, edge style = {red}]{3}{6}{I}
	\depedge[edge above, edge style = {red}]{2}{1}{D}
	\depedge[edge above, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, edge style = {red}]{6}{7}{P}
	\depedge[edge above, edge style = {red}]{8}{9}{J}
	\deproot[edge above, edge style = {red}]{2}{W}
	\deproot[edge above, edge style = {red}]{7}{WV}
	\deproot[edge above, edge style = {red}]{10}{X}
	\depedge[edge above, edge style = {red}]{6}{4}{E}
	\depedge[edge above, edge style = {red}]{6}{5}{E}
  \end{dependency}

  \caption{Directionalize the edges}
\end{figure}
}

\frame{\frametitle{Link Grammars}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, edge style = {blue}]{3}{\small ROOT}
	\depedge[edge below, edge style = {red}]{2}{3}{S}
	\depedge[edge above, edge style = {blue}]{3}{2}{\small SBJ}
	\depedge[edge above, edge style = {blue}]{3}{4}{\small ADV}
	\depedge[edge above, edge style = {blue}]{3}{5}{\small ADV}
	\depedge[edge below, edge style = {red}]{3}{6}{I}
	\depedge[edge above, edge style = {blue}]{3}{6}{\small VC}
	\depedge[edge above, edge style = {blue}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, edge style = {red}]{2}{1}{D}
	\depedge[edge above, edge style = {blue}]{2}{1}{\small NMOD}
	\depedge[edge below, edge style = {red}]{7}{8}{MV}
	\depedge[edge above, edge style = {blue}]{7}{8}{\small ADV}
	\depedge[edge below, edge style = {red}]{6}{7}{P}
	\depedge[edge above, edge style = {blue}]{6}{7}{\small VC}
	\depedge[edge below, edge style = {red}]{8}{9}{J}
	\depedge[edge above, edge style = {blue}]{8}{9}{\small PMOD}
	\deproot[edge below, edge style = {red}]{2}{W}
	\deproot[edge below, edge style = {red}]{7}{WV}
	\deproot[edge below, edge style = {red}]{10}{X}
	\depedge[edge below, edge style = {red}]{6}{4}{E}
	\depedge[edge below, edge style = {red}]{6}{5}{E}
  \end{dependency}

  \caption{Compare resulting dependency parse with Penn Treebank annotations}
\end{figure}

\frame{\frametitle{Link Grammars}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, edge style = {blue, dotted}]{3}{\small ROOT}
	\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge above, edge style = {blue, dotted}]{3}{4}{\small ADV}
	\depedge[edge above, edge style = {blue, dotted}]{3}{5}{\small ADV}
	\depedge[edge below, edge style = {red, thick}]{3}{6}{I}
	\depedge[edge above, edge style = {blue, thick}]{3}{6}{\small VC}
	\depedge[edge above, edge style = {blue, dotted}, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, edge style = {red, thick}]{2}{1}{D}
	\depedge[edge above, edge style = {blue, thick}]{2}{1}{\small NMOD}
	\depedge[edge below, edge style = {red, thick}]{7}{8}{MV}
	\depedge[edge above, edge style = {blue, thick}]{7}{8}{\small ADV}
	\depedge[edge below, edge style = {orange, thick}]{6}{7}{P}
	\depedge[edge above, edge style = {blue, thick}]{6}{7}{\small VC}
	\depedge[edge below, edge style = {red, thick}]{8}{9}{J}
	\depedge[edge above, edge style = {blue, thick}]{8}{9}{\small PMOD}
	\deproot[edge below, edge style = {red, dotted}]{2}{W}
	\deproot[edge below, edge style = {orange, ultra thick, dotted}]{7}{WV}
	\deproot[edge below, edge style = {red, dotted}]{10}{X}
	\depedge[edge below, edge style = {red, dotted}]{6}{4}{E}
	\depedge[edge below, edge style = {red, dotted}]{6}{5}{E}
  \end{dependency}

  \caption{Compare resulting dependency parse with Penn Treebank annotations}
\end{figure}
